Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO$_2$ Reduction Reactions

### 2024-01-06 paper/main_sections/3_introduction.tex
add cross-ref in main text
revise fig names

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{main_sections/figures/figure_1.png}
    \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
    The figure demonstrates the integrated usage of volcano plots for predictive assessments of existing catalysts and the utility of CNNs to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
    Advanced occlusion and shifting experiments on eDOS are conducted to extract chemical meanings from CNN model.}
    \label{main_fig1:pipeline}
\end{figure}

@@

In this study, we introduced a catalyst performance analysis pipeline (Figure 1) integrating a customized CNN model and volcano plots.
Our CNN model accurately estimated the adsorption energies, the activity descriptor, from the eDOS of 2D materials supported single metal catalysts.
Evaluations on the adsorption energies of nine intermediates along CO$_2$RR and competing hydrogen evolution reaction (HER) as well yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV, which is well aligned with the precision of conventional DFT calculations \cite{kirklin2015open, lejaeghere2016reproducibility, wellendorff2015benchmark}.
This result validated the capability of current CNN model to accurately capture intricate spatial information from eDOS.
Building on this, we introduced an orbitalwise eDOS occlusion experiment was adopted afterwards inspired from the occlusion technique widely used in computer vision and pattern recognition applications.
Systematic eDOS experiment was performed to elucidate orbitalwise contributions to the adsorption energies at different energy levels, which produced consistent outcome from Crystal Orbital Hamilton Population (COHP) analysis and real-space wavefunction visualization.
All these results justified the proficiency of CNN model on identifying the dominant orbitals for adsorbate-substrate interactions.
Furthermore, orbital-wise eDOS shifting experiment, exploring the impact of orbital-wise eDOS shifting on the adsorption behavior of studied catalysts were performed.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{main_sections/figures/main_fig1_pipeline.JPG}
    \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
    The figure demonstrates the integrated usage of volcano plots for predictive assessments of existing catalysts and the utility of CNNs to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
    Advanced occlusion and shifting experiments on eDOS are conducted to extract chemical meanings from CNN model.}
    \label{main_fig1:pipeline}
\end{figure}

@@

In this study, we introduced a catalyst performance analysis pipeline (\cref{main_fig1:pipeline}) integrating a customized CNN model and volcano plots.
Our CNN model accurately estimated the adsorption energies, the activity descriptor, from the eDOS of 2D materials supported single metal catalysts.
Evaluations on the adsorption energies of nine intermediates along CO$_2$RR and competing hydrogen evolution reaction (HER) as well yielded prediction mean absolute errors (MAEs) at the level of 0.1 eV, which is well aligned with the precision of conventional DFT calculations \cite{kirklin2015open, lejaeghere2016reproducibility, wellendorff2015benchmark}.
This result validated the capability of current CNN model to accurately capture intricate spatial information from eDOS.
Building on this, we introduced an orbitalwise eDOS occlusion experiment was adopted afterwards inspired from the occlusion technique widely used in computer vision and pattern recognition applications.
Systematic eDOS experiment was performed to elucidate orbitalwise contributions to the adsorption energies at different energy levels, which produced consistent outcome from Crystal Orbital Hamilton Population (COHP) analysis and real-space wavefunction visualization.
All these results justified the proficiency of CNN model on identifying the dominant orbitals for adsorbate-substrate interactions.
Furthermore, orbital-wise eDOS shifting experiment, exploring the impact of orbital-wise eDOS shifting on the adsorption behavior of studied catalysts were performed.
